\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-10 manuscript.Rmd

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
packrat::snapshot()
```

@@

knitr::opts_chunk$set(include = FALSE)
library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
#library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)

r_refs("references.bib")
```

@@

```{r FlowchartFig, fig.align='center', fig.cap='Development', include=FALSE, out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

```{r tabDes, results='asis'}
apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
```

@@

```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
knitr::include_graphics('Manuscript.figures/parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('Manuscript.figures/Hull.png')

@@

```{r EFAplotcode, include=FALSE}
#library(DiagrammeR)
EFAplot.LR <- grViz("
digraph boxes_and_circles {

@@

export_svg(EFAplot.LR) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.LR.png")

@@

```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
knitr::include_graphics('Manuscript.figures/EFAplot.LR.png')

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a]. Commonly used Model fit suggestions of [@huCutoffCriteriaFit1999] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit. The chi-square test is also used to estimate the absolute model fit. Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model. The fitted model failed to attain an absolute fit estimated by the chi-square test. However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@RN1231]. The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272]. Subsequently, we judged the model fit based on the incremental fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).  Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI])   and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.

@@

apa_table(CFa.matrix, caption = "Fit indices of CFA")

@@

```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE}
library(semPlot)

@@

```{r Invarianceshortcut, include=FALSE}
#library("semTools")
invariance.model <- measurementInvariance(model = LB.model.Cor.2,
                                          data = invariance.data,
                                          group = "English_Speaking",
                                          ordered =   names(CFA.data),
                                          estimator = "WLSMV",
                                          strict = T)
invariance.model$fit.configural
```

@@

LB.model.Cor.3 <- "F1 =~ a1*item16 + a2*item36 + item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a4*item32 +a3*item35 + item38+ item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1 
                       a1==a2
                       a4==a3
                item30 ~~  item41
F4~~1*F4"

@@

Invariance.table <- compareLavaan(models,
              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
              fitmeas = c("chisq", "df", "pvalue", "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
              scaled = TRUE,
              chidif = TRUE, digits = 2)

@@

```{r Invariance Tab}
apa_table(Invariance.table)
```

>>>>

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
#packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
```

```{r eval=FALSE, include=FALSE}
#if "packrat" doesnot work you can run this chunk manually to get all required packs"

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("car")
install.packages("semTable")
install.packages("magick")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
#library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
r_refs("references.bib")
```

@@

```{r FlowchartFig, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

```{r tabDes}
apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
```

@@

```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", out.height="50%", out.width="50%"}
knitr::include_graphics('Manuscript.figures/parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('Manuscript.figures/Hull.png')

@@

```{r EFAplotcode, include=FALSE}
#library(DiagrammeR)
EFAplot <- grViz("
digraph boxes_and_circles {

@@

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.png")

@@

```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="100%", out.width="120%"}
knitr::include_graphics('Manuscript.figures/EFAplot.png')

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a]. Commonly used Model fit suggestions of [@huCutoffCriteriaFit1999] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit. The chi-square test is also used to estimate the absolute model fit. Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model. The fitted model failed to attain an absolute fit estimated by the chi-square test. However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015]. The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272]. Subsequently, we judged the model fit based on the incremental fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).  Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI])   and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.

@@

apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T)

@@

```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE}
#library(semPlot)

@@

@@

@@

Invariance.table <- compareLavaan(models,
              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
              scaled = T,
              chidif = T, digits = 2)

colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "SRMR", "Chi-Sqr comparison", "df*", "p")

@@

```{r InvarianceTab}
apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
